Decade of Lost Precision: A General Framework For Image Feature Matching Without Geometric Constraints

### 2014-11-27 paper.tex
Fixed wording for assumption #2

The empirical results of \emph{Self-Match} in Figure~\ref{fig:all_objects} and Figure~\ref{fig:patches} support the assumption. \emph{Self-Match} discards any match where a feature in the query image is more similar to the query feature, yet the algorithm consistently performs equally well or better than \emph{Ratio-Match} supporting the notion that for most all true correspondences the best match is found in the \emph{target image}. We note that even at high recall rates where we find the more challenging matches, this assumption is still supported by the empirical results with \emph{Self-Match} performing on par with \emph{Ratio-Match}.

@@

\begin{figure*}[t]
	\centering
    \includegraphics[width=\columnwidth]{images/results_all_objects}
    \caption{Results for the 3D objects dataset. Each plot 
    contains the average of 84 objects photographed under 3 
different lighting conditions.}
    \label{fig:all_objects}
\end{figure*}

Figure~\ref{fig:all_objects} shows the performance of the different matching methods in our proposed framework for $12$ increasingly bigger angle differences. The results are shown in a precision / recall plot to make it easy to compare performance in terms of precision at similar levels of recall.  For each plot we show the averaged results on all 3D objects, with equal weight given to the result from each image.

>>>>

The empirical results of \emph{Self-Match} in Figure~\ref{fig:all_objects} and Figure~\ref{fig:patches} support the assumption. \emph{Self-Match} discards any match where a feature in the query image is more similar to the query feature, yet the algorithm consistently performs equally well or better than \emph{Ratio-Match} supporting the notion that for almost all true correspondences the best match is found in the \emph{target image}. As we would expect this assumption breaks down as we increase \tau to accept matches with higher uniqueness ratios, illustrated by the higher recall rates of \emph{Ratio-Match} compared to \emph{Self-Match} in most plots. Once we accept almost all proposed nearest neighbors as matches we are bound to encounter more non-distinct feature points for which even true correspondences might have better matches amongst the \emph{query features}.

@@

\begin{figure*}[t]
	\centering
    \includegraphics[width=\columnwidth]{images/results_all_objects}
    \caption{Results for the 3D objects dataset. Each plot 
    contains the results of 84 objects photographed under 3 
different lighting conditions averaged over each image pair.}
    \label{fig:all_objects}
\end{figure*}

Figure~\ref{fig:all_objects} shows the performance of the different matching methods in our proposed framework for $12$ increasingly bigger angle differences. The results are shown in a precision / recall plot to make it easy to compare performance in terms of precision at similar levels of recall.  For each plot we show the averaged results on all 3D objects, with equal weight given to each image pair.
